---
title: "Check Analysis Datasets"
output: html_notebook
---

The entire purpose of this notebook is to check our analysis datasets for weird
values, mistakes, etc.

```{r setup}
load("AnalysisData/iculib.Rdata")

library(Hmisc)
options(grType = "plotly")

```

```{r describe_objs}
## Raw data from REDCap - mostly just checking for extremes
desc_demog_rc <-
  describe(demog[,1:grep("demographic_and_discharge_form_complete_f",
                         names(demog),
                         fixed = TRUE)])

## Calculated variables
desc_demog_calc <-
  describe(demog[,(grep("demographic_and_discharge_form_complete_f",
                        names(demog),
                        fixed = TRUE) + 1):ncol(demog)])

desc_compliance_rc <- 
  describe(compliance[,1:grep("daily_compliance_form_complete_f",
                              names(compliance),
                              fixed = TRUE)])
desc_compliance_calc <- 
  describe(compliance[,(grep("daily_compliance_form_complete_f",
                             names(compliance),
                             fixed = TRUE) + 1):ncol(compliance)])

desc_tsdata <- describe(tsdata)

```

# Descriptives of `demog` dataset (one record per patient)

## Raw variables from REDCap

```{r print_desc_demog_rc}
html(desc_demog_rc, size=80, scroll=TRUE)

plot(desc_demog_rc)

```

## Calculated variables

```{r print_desc_demog_calc}
html(desc_demog_calc, size=80, scroll=TRUE)

plot(desc_demog_calc)

```

# Descriptives of `compliance` dataset (many records per patient)

## Raw variables from REDCap

```{r print_desc_compliance_rc}
html(desc_compliance_rc, size=80, scroll=TRUE)

plot(desc_compliance_rc)

```

## Calculated variables

```{r print_desc_compliance_calc}
html(desc_compliance_calc, size=80, scroll=TRUE)

plot(desc_compliance_calc)

```

# Descriptives of `tsdata` dataset (one record per month)

```{r print_desc_tsdata}
html(desc_tsdata, size=80, scroll=TRUE)

plot(desc_tsdata)

```

